Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-23 Grassmannian_cells.tex
test
Section 3.2 edits and notation changes up to Lemma 3.36

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $d$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   % \item The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the second statement.

%For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$. As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
%\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
%\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
%As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}
\begin{remark}
  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
%Lemma~\ref{le:hom equivariance} gives an identification of $\Gr(H_m)$ with $\Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
For $1\le r\le n-1$, let $\Gr_r(H_m)\subset \Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.

For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

@@

\subsection{Lifting to $\widetilde{K(n)}$}\label{Lifting}

@@

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
Set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.\]
Depending on context (more specifically the parity of $m+1$ below), we will sometimes identify the word $(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, we associate to each $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$, $1\leq k\leq m$, a preprojective subrepresentation $\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations 
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom_{K(n)}(P_m,P_{m+1})\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For every $\ui\in A_1^{(l)}$, there exists a truncated preprojective representation $\tilde P_{m+1}^\ui$ which is the cokernel of
      \begin{align}
        \label{ses1}
        \ses{\bigoplus_{j=1}^l \tilde P_{m,i_j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\ui}}.
      \end{align}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first part is immediate from Theorem~\ref{covering}.
  The second part is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq k\leq n$, we have 
  $$\CC=\Hom_{K(n)}(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom_{\widetilde{K(n)}}(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

  For the final claim, observe that under the isomorphism from part (1) the sequence $\ui\in A_1^{(l)}$ corresponds to an $l$-dimensional subspace $V\in H_m$.
  The map $\bigoplus_{j=1}^l \tilde P_{m,i_j}\to \tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^\ui$.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  For $m\geq 2$ and $\uj\in I_l$, the following hold:
  \begin{enumerate}
    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.

  The second identities are an immediate consequence of Lemma \ref{le:basic homological properties}, but can also be obtained when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).
%  As $\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the identities in the second statement follow when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).

  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\CC$. Thus applying $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\underline{\quad})$ to (\ref{ses1}) yields $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional. In view of the second identity, we obtain the third identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$ to (\ref{ses1}).
\end{proof} 
%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

@@

\begin{theorem}
  The Euler characteristic $\chi(\Gr_e(P_m^{[k]}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{[k]}$.
\end{theorem}
\begin{proof}
  We proceed by induction.
  The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{[n-1]}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\emptyset,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
  As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.

  Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{[k]}$ (resp. $\tilde P_{m+1}^{[k]}$) and consider the short exact sequence
  \[
    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
  \]
  Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{[k]}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{[k]}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
  Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{[k]})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{[k]}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{[k]}})_0=\emptyset$.
  But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{[k]}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{[k]}}$ by a $2$-arrow.
\end{proof}

>>>>

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are exact for any $n\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $d$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the second statement.
\end{proof}
\begin{remark}
  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.
Write $\Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $\Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
For $1\le r\le n-1$, let $\Gr_r(H_m)\subset \Gr(H_m)$ be the subvariety of $r$-dimensional subspaces of $H_m$.

For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.
\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
\begin{proof}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

@@

\subsection{Lifting to $\widetilde{K(n)}$}
\label{Lifting}

@@

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
For $l\ge1$, set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_{j+1}\text{ for } 1\le j<l\}.\]
Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$ we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
      \end{equation}
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  The first part is immediate from Theorem~\ref{covering}.
  The second part is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC=\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

  For the final claim, observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to a subspace $V\in H_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_m,P_{m+1})$ which is compatible with the direct sum decomposition from part (1).
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\notin I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})=\CC.\] 
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)=\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item We have $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}(2).
  Now the middle space is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
  Part (3) then follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1}.
\end{proof}

Note that by Lemma~\ref{le:properties}(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]

@@

\begin{theorem}
  The Euler characteristic $\chi(\Gr_e(P_m^{[k]}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{[k]}$.
\end{theorem}
\begin{proof}
  We proceed by induction.
  The strong successor closed subsets of the $2$-quivers of $P_1$, $P_2$ and $P_2^{[n-1]}$ coincide with the successor closed subsets of the coefficient quivers (\ref{coeff}) which we denote by $\Gamma_M$ for $M\in\{P_1, P_2,P_2^{[n-1]}\}$.
  Passing to the universal cover, we have $\Gr_e(\tilde M)\in\{\varnothing,\{\pt\}\}$ such that $\Gr_e(\tilde M)=\{\pt\}$ if and only if $e\subset (\Gamma_M)_0$ is successor closed.
  As the number cells of $\Gr_e(\tilde M)$ and $\Gr_e(M)$ coincide, the claim follows.

  Thus assume that the claim is true for $P_m$ (resp. $\tilde P_{m}$) and $P_{m+1}^{[k]}$ (resp. $\tilde P_{m+1}^{[k]}$) and consider the short exact sequence
  \[
    \ses{\tilde P_m}{\tilde P_{m+1}^{[k-1]}}{\tilde P_{m+1}^{[k]}}.
  \]
  Denote the corresponding $2$-quivers by $\Gamma_{P_m}$ and $\Gamma_{P_{m+1}^{[k]}}$ and let $\beta_1\cup\beta_2\subset (\Gamma_{P_m})_0\cup (\Gamma_{P_{m+1}^{[k]}})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cell by induction hypothesis.
  Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
  By Proposition \ref{fibers} the pair $\beta_1\cup\beta_2$, it does not correspond to a non-empty cell of $\Gr_{d(\beta_1+\beta_2)}(\tilde P_{m+1}^{[k]})$ if and only if $\beta_2=(\Gamma_{P_{m+1}^{[k]}})_0$ and $\beta_1\cap(\Gamma_{\tau\tilde P_{m+1}^{[k]}})_0=\varnothing$.
  But this is precisely the condition on $\beta_1\cup\beta_2$ to be strong successor closed as $\Gamma_{P_{m+1}^{[k]}}$ is connected to $\Gamma_{\tau\tilde P_{m+1}^{[k]}}$ by a $2$-arrow.
\end{proof}
